Appendix A: Simulation Details and Results

### 2014-08-04 supp/sim_tables_appendix.tex
Small revisions; added line numbers to response

\documentclass{article}
\usepackage[letterpaper,hmargin={2.4cm,2.4cm},vmargin={2.4cm,2.4cm}]{geometry}
\usepackage[pdftex]{hyperref}
\usepackage{soul}
\usepackage{graphicx}
\usepackage{amsmath}
%\usepackage{rotating}
\usepackage{pdflscape}

@@

The third simulation was a Gompertz-logistic model with two non-overlapping generations per year (sampling occasion).   
We used 200 sites for 25 years, and data-generating values of $\Lambda = 10$, $r = 0.05$, $K = 10$, and $p = 0.5$.
We estimated parameters with the Gompertz-logistic model with 
one generation per year using both maximum likelihood and MCMC approaches, as well
as allowing for two generations per year with MCMC.  
For the maximum likelihood model, we used finite upper bound $N_{max} = 150$. 
For the Bayesian framework we used non-informative priors ($\Lambda$ and $K  \sim \mathrm{U}(0, 30)$, $r  \sim \mathrm{U}(0, 5)$,
and $p  \sim \mathrm{U}(0, 1)$.  
For model and simulation we ran a single chain. We sampled the MCMC for 20,000 iterations, after 1,000 adaptation and tuning samples.

@@

%\section*{Simulation Setup and Results Tables}
\begin{table}[t]
  \centering
\caption{Changed parameter values, by series of simulations.  We
simulated 1000 sets of data each combination of parameter values
for 100 sites over 40 years.  We assumed that initial abundance
($\Lambda$) was Poisson distributed.  For the exponential 
simulations we included all combinations of low, medium, and
high $\Lambda$, growth rate ($r$), and detection probability ($p$).
For the Ricker-logistic model simulations we used $\Lambda$ = 10 and $p$ = 0.25, and
simulated low, medium, and high values of $r$ and equilibrium density ($K$).
For the Ricker-logistic + immigration dynamics model we fixed all parameters the
same as the Ricker-logistic model (with $r$ = 0.05 and $K$ = 10) and
simulated low, medium, and high values of immigration rate ($\iota$).}  
\begin{tabular}{lcccccccc}
    \hline
    & \multicolumn{3}{c}{Exponential Growth} && \multicolumn{2}{c}{Ricker-logistic} &&
    Ricker-logistic + Immigration \\
    \cline{2-4}     \cline{6-7}    \cline{9-9}
& $\Lambda$ & $r$ & $p$ && $r$  & $K$ && $\iota$  \\    
\hline
    Low	        &1	&-0.01	&0.05	&&0.005	 &5	&&0.005  \\
    Med	        &5	&0	&0.25	&&0.05	&10	&&0.05   \\
    High		 &10 &0.005	&0.5	&&0.1	&20	&&0.5    \\
    \hline
  \end{tabular}
\end{table}

@@

\clearpage
\begin{table}
  \centering
  \footnotesize
  \caption{Simulation results from 3 cases of Ricker-logistic and immigration dynamics with 1000 Monte Carlo replicates for each.}
  \begin{tabular}{cccccccccccccccccccc}
    \hline
    \multicolumn{5}{c}{Data generating values}&
    \multicolumn{5}{c}{Mean} &
    \multicolumn{5}{c}{RMSE} &
    \multicolumn{5}{c}{Coverage} \\
    \multicolumn{5}{c}{\rule{4cm}{1pt}} &
    \multicolumn{5}{c}{\rule{7cm}{1pt}} &
    \multicolumn{5}{c}{\rule{7cm}{1pt}} &
    \multicolumn{5}{c}{\rule{4cm}{1pt}} \\
%    \hline
    $\Lambda$ & $r$ & $K$ & $\iota$ & $p$ & $\Lambda$ & $r$ & $K$ & $\iota$ & $p$ & $\Lambda$ & $r$ & $K$ &
    $\iota$ & $p$ & $\Lambda$ & $r$ & $K$ & $\iota$ & $p$ \\
    \hline
10 &0.05 &10 &0.005 &0.25  &9.997 &0.05148 &9.687 &0.00510 &0.25077 &0.87742 &0.01805 &1.77679 &0.00315 &0.01795  &0.951 &0.944 &0.964 &0.947 &0.942\\
10 &0.05 &10 &0.050 &0.25 &10.015 &0.05166 &9.758 &0.05039 &0.25070 &0.87490 &0.01731 &1.72376 &0.01055 &0.01839  &0.943 &0.932 &0.958 &0.940 &0.943\\
10 &0.05 &10 &0.500 &0.25 &10.000 &0.05057 &9.648 &0.50811 &0.25110 &0.96491 &0.01942 &2.68264 &0.07763 &0.02050  &0.947 &0.940 &0.952 &0.951 &0.941\\
  \hline
  \end{tabular}
  \label{tab:simricki}
\end{table}
\clearpage

@@

\begin{table}[htb]
  \centering
  \footnotesize
  \caption{Parameters of Gompertz-logistic simulation with two generation per year 
(1000 Monte Carlo replicates)
  and results of models fit to these data.}
  \begin{tabular}{lcccccccccccccc}
    \hline
    & \multicolumn{4}{c}{Mean} &&
    \multicolumn{4}{c}{RMSE} &&
    \multicolumn{4}{c}{Coverage} \\
    \cline{2-5}     \cline{7-10}    \cline{12-15}
    Model & $\Lambda$ & $r$ & $K$ & $p$ &&
    $\Lambda$ & $r$ & $K$ & $p$ && 
    $\Lambda$ & $r$ & $K$ & $p$ \\
    \hline
Simulation & 
10	&0.05	&10	&0.5	&&-	&-	&-	&-	&&-	&-	&-	&-\\
Gompertz-logistic (MLE; 1 generation/year) &
8.392	&0.00919	&1.269	&0.60241	&&
1.64842	&-	&8.94192	&0.10395	&&
0.013	&-	&1.000 	&0.000 \\
Gompertz-logistic (MCMC; 1 generation/year) &
8.315	&0.03044	&4.575	&0.60723	&&
1.72224	&-	&5.70813	&0.10870	&&
0.007	&-	&0.368		&0.000 \\
Gompertz-logistic (MCMC; 2 generations/year) &
9.969	&0.05405	&10.407	&0.50337	&&
0.55084	&0.01697	&2.26087	&0.02318	&&
0.921	&0.964	&0.967	&0.935 \\
  \hline
  \end{tabular}
  \label{tab:simgomp}
\end{table}

@@

\begin{figure}
\caption{Histograms of 1000 parameter estimates for each of nine
simulation cases with Ricker-logistic dynamics. The blue vertical lines are the 
data-generating values.}
  \centering
  \includegraphics{../figs/rick_hists}
\label{fig:rick_hists}
\end{figure}

\begin{figure}
\caption{Histograms of 1000 parameter estimates for each of three
simulation cases with Ricker-logistic + immigration dynamics. The blue vertical lines are the 
data-generating values.}
  \centering
  \includegraphics[width=8.5in]{../figs/ricki_hists}
\label{fig:ricki_hists}
\end{figure}

@@

\begin{figure}
\caption{Histograms of 1000 parameter estimates simulated with Gompertz-logistic dynamics, 
two generations per year, fit with three different Gompertz-logistic models.
The vertical lines are the data-generating values; changing the number of generations
changes the meaning of $r$, so no data-generating values of it are provided for the 
single generation per year cases.}
  \centering
  \includegraphics{../figs/gomp_hists}
\label{fig:gomp_hists}
\end{figure}
\end{landscape}

>>>>

\documentclass{article}
\usepackage[letterpaper,hmargin={2.4cm,2.4cm},vmargin={2.4cm,2.4cm}]{geometry}
\usepackage[pdftex,hidelinks]{hyperref}
\usepackage{soul}
\usepackage{graphicx}
\usepackage{amsmath}
%\usepackage{rotating}
\usepackage{pdflscape}

@@

The third simulation was a Gompertz model with two non-overlapping generations per year (sampling occasion).   
We used 200 sites for 25 years, and data-generating values of $\Lambda = 10$, $r = 0.05$, $K = 10$, and $p = 0.5$.
We estimated parameters with the Gompertz model with 
one generation per year using both maximum likelihood and MCMC approaches, as well
as allowing for two generations per year with MCMC.  
For the maximum likelihood model, we used finite upper bound $N_{max} = 150$. 
For the Bayesian framework we used non-informative priors ($\Lambda$ and $K  \sim \mathrm{U}(0, 30)$, $r  \sim \mathrm{U}(0, 5)$,
and $p  \sim \mathrm{U}(0, 1)$.  
For model and simulation we ran a single chain. We sampled the MCMC for 20,000 iterations, after 1,000 adaptation and tuning samples.

@@

%\section*{Simulation Setup and Results Tables}
\begin{table}[t]
  \centering
\caption{Changed parameter values, by series of simulations.  We
simulated 1000 sets of data each combination of parameter values
for 100 sites over 40 years.  We assumed that initial abundance
($\Lambda$) was Poisson distributed.  For the exponential 
simulations we included all combinations of low, medium, and
high $\Lambda$, growth rate ($r$), and detection probability ($p$).
For the Ricker model simulations we used $\Lambda$ = 10 and $p$ = 0.25, and
simulated low, medium, and high values of $r$ and equilibrium density ($K$).
For the Ricker + immigration dynamics model we fixed all parameters the
same as the Ricker model (with $r$ = 0.05 and $K$ = 10) and
simulated low, medium, and high values of immigration rate ($\iota$).}  
\begin{tabular}{lcccccccc}
    \hline
    & \multicolumn{3}{c}{Exponential Growth} && \multicolumn{2}{c}{Ricker} &&
    Ricker + Immigration \\
    \cline{2-4}     \cline{6-7}    \cline{9-9}
& $\Lambda$ & $r$ & $p$ && $r$  & $K$ && $\iota$  \\    
\hline
    Low	        &1	&-0.01	&0.05	&&0.005	 &5	&&0.005  \\
    Med	        &5	&0	&0.25	&&0.05	&10	&&0.05   \\
    High		 &10 &0.005	&0.5	&&0.1	&20	&&0.5    \\
    \hline
  \end{tabular}
\end{table}

@@

\clearpage
\begin{table}
  \centering
  \footnotesize
  \caption{Simulation results from 3 cases of Ricker and immigration dynamics with 1000 Monte Carlo replicates for each.}
  \begin{tabular}{cccccccccccccccccccc}
    \hline
    \multicolumn{5}{c}{Data generating values}&
    \multicolumn{5}{c}{Mean} &
    \multicolumn{5}{c}{RMSE} &
    \multicolumn{5}{c}{Coverage} \\
    \multicolumn{5}{c}{\rule{4cm}{1pt}} &
    \multicolumn{5}{c}{\rule{7cm}{1pt}} &
    \multicolumn{5}{c}{\rule{7cm}{1pt}} &
    \multicolumn{5}{c}{\rule{4cm}{1pt}} \\
%    \hline
    $\Lambda$ & $r$ & $K$ & $\iota$ & $p$ & $\Lambda$ & $r$ & $K$ & $\iota$ & $p$ & $\Lambda$ & $r$ & $K$ &
    $\iota$ & $p$ & $\Lambda$ & $r$ & $K$ & $\iota$ & $p$ \\
    \hline
10 &0.05 &10 &0.005 &0.25  &9.997 &0.05148 &9.687 &0.00510 &0.25077 &0.87742 &0.01805 &1.77679 &0.00315 &0.01795  &0.951 &0.944 &0.964 &0.947 &0.942\\
10 &0.05 &10 &0.050 &0.25 &10.015 &0.05166 &9.758 &0.05039 &0.25070 &0.87490 &0.01731 &1.72376 &0.01055 &0.01839  &0.943 &0.932 &0.958 &0.940 &0.943\\
10 &0.05 &10 &0.500 &0.25 &10.000 &0.05057 &9.648 &0.50811 &0.25110 &0.96491 &0.01942 &2.68264 &0.07763 &0.02050  &0.947 &0.940 &0.952 &0.951 &0.941\\
  \hline
  \end{tabular}
  \label{tab:simricki}
\end{table}
\clearpage

@@

\begin{table}[htb]
  \centering
  \footnotesize
  \caption{Parameters of Gompertz simulation with two generation per year 
(1000 Monte Carlo replicates)
  and results of models fit to these data.}
  \begin{tabular}{lcccccccccccccc}
    \hline
    & \multicolumn{4}{c}{Mean} &&
    \multicolumn{4}{c}{RMSE} &&
    \multicolumn{4}{c}{Coverage} \\
    \cline{2-5}     \cline{7-10}    \cline{12-15}
    Model & $\Lambda$ & $r$ & $K$ & $p$ &&
    $\Lambda$ & $r$ & $K$ & $p$ && 
    $\Lambda$ & $r$ & $K$ & $p$ \\
    \hline
Simulation & 
10	&0.05	&10	&0.5	&&-	&-	&-	&-	&&-	&-	&-	&-\\
Gompertz (MLE; 1 generation/year) &
8.392	&0.00919	&1.269	&0.60241	&&
1.64842	&-	&8.94192	&0.10395	&&
0.013	&-	&1.000 	&0.000 \\
Gompertz (MCMC; 1 generation/year) &
8.315	&0.03044	&4.575	&0.60723	&&
1.72224	&-	&5.70813	&0.10870	&&
0.007	&-	&0.368		&0.000 \\
Gompertz (MCMC; 2 generations/year) &
9.969	&0.05405	&10.407	&0.50337	&&
0.55084	&0.01697	&2.26087	&0.02318	&&
0.921	&0.964	&0.967	&0.935 \\
  \hline
  \end{tabular}
  \label{tab:simgomp}
\end{table}

@@

\begin{figure}
\caption{Histograms of 1000 parameter estimates for each of nine
simulation cases with Ricker dynamics. The blue vertical lines are the 
data-generating values.}
  \centering
  \includegraphics{../figs/rick_hists}
\label{fig:rick_hists}
\end{figure}

\begin{figure}
\caption{Histograms of 1000 parameter estimates for each of three
simulation cases with Ricker + immigration dynamics. The blue vertical lines are the 
data-generating values.}
  \centering
  \includegraphics[width=8.5in]{../figs/ricki_hists}
\label{fig:ricki_hists}
\end{figure}

@@

\begin{figure}
\caption{Histograms of 1000 parameter estimates simulated with Gompertz dynamics, 
two generations per year, fit with three different Gompertz models.
The vertical lines are the data-generating values; changing the number of generations
changes the meaning of $r$, so no data-generating values of it are provided for the 
single generation per year cases.}
  \centering
  \includegraphics{../figs/gomp_hists}
\label{fig:gomp_hists}
\end{figure}
\end{landscape}
